Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-21 paper/paper.tex
WIP discussion

Solving analytically for the wavenumber requires dropping spatial gradients of
$k$ in Eq. \ref{eq:wavenumber} and assuming homogeneous $g$:

@@

@@

\backsection[Data availability statement]{
  The data and code to generate the figures and run the numerical simulations
  are available at [TODO].
  The numerical model is available as a standalone package at [TODO].
  %See JFM's \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/journal-policies/research-transparency}{research transparency policy} for more information
}

>>>>

Solving analytically for the wavenumber requires dropping the spatial derivatives
of $k$ in Eq. \ref{eq:wavenumber} and assuming homogeneous $g$:

@@

Limitations of this study; no wind or dissipation. Only considering deep water
gravity waves, but the results could be extended to gravity-capillary waves
in arbitrary depth.
Although it is impossible to isolate the hydrodynamic modulation effects
from other modulation effects in the field and laboratory data, it is
nevertheless useful to study this process in isolation from other processes
in a theoretical and numerical framework.

Discuss that we examined r = 10, 100 and find very similar results,
consistent with \citet{longuet1987propagation}

Results are very similar to prior work, but provide an easy to use analytical
solution to calculate modulations without numerical iteration.

Discuss the group velocity results of \citet{Willebrand1975energy}.
What do we get for group velocity modulation?
Should the short-wave modulations be considered for inclusion in spectral wave
models?

Implications for spectral wave models and wind input to short waves.

@@

\backsection[Data availability statement]{
  The code to run the numerical simulations and generate the figures in this
  paper is available at \url{https://github.com/wavesgroup/wave-modulation-paper}.
  The numerical model is available as a standalone package at
  \url{https://github.com/wavesgroup/2wave}.
  %See JFM's \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/journal-policies/research-transparency}{research transparency policy} for more information
}
